A neural coarse graining theory of consciousness

### 2018-10-26 Paper_neural_coarse_graining_of_consciousness.tex
After PF from Ryota for chapter 1

		%% Story about a cell
		Imagine you are a neuron in Alice's brain. Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons. However, you have no idea that you are one of neurons in Bill's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup. You are totally ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.

		A similar story also happens to Alice's conscious mind. To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action. However, her conscious experience does not show the dynamic of your membrane potential and about action potentials you send to other neurons every second. That is, information in Alice's conscious experience does not contain information involved in your information processing.

@@

		%% scale
		It seems to be true that we are unable to consciously access information processed at every scale in the neural system. Only information at certain levels of coarse-graining can become conscious contents. At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}. However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious contents shows astonishing stability and high robustness against to ubiquitous noise in the neural system \citep{mathis1995computational}. Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system may contributes conscious experience very little (cerebellum for example \citep{lemon2010life}). Additionally, we don't experience "super-consciousness" when we have massive inter-individual interactions with other human-beings. Even though evidence has shown several types of collective information processing at human social groups levels \citep{malone2015handbook}. information processed at this level seems to depart from our individual conscious contents.

		%% our argument			
		In this article, we propose a new theory of consciousness, called \ac{\tname}. This proposal states that consciousness does not rest to particular neural architectures or location of the neural system. Instead, we argue that consciousness correlates information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure (NTIC). We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		%% About this paper			
		Our theory rests on two core concepts: non-trivial informational closure and neural coarse-graining. In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents. We next argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level. We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory. We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness. Finally, we provide predictions and testable approaches for this theory.

%				@ \todo{Do I need a figure?}
%					\begin{figure}
%						\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
%						\cite{pennartz2017consciousness}
%						\caption{xxxx}
%	   			   	\end{figure}

>>>>

		%% Story about a cell
		Imagine you are a neuron in Alice's brain. Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons. However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup. You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
		A similar story also applies to Alice's conscious mind. To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action. However, her conscious experience does not show the dynamic of your membrane potential and about action potentials you send to other neurons every second. That is, information in Alice's conscious experience does not contain information involved in your information processing.

@@

		%% scale
		It seems to be true that we are unable to consciously access information processed at every scale in the neural system. Only information at certain levels of coarse-graining can become conscious contents. At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}. However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}. Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}). Additionally, we do not  experience "super-consciousness" when we have massive inter-individual interactions with other human-beings. Even though evidence has shown several types of collective information processing at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.

		%% our argument		
		In this article, we propose a new theory of consciousness, called\ac{\tname}. This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems. Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC). We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		%% About this paper			
		Our theory rests on two core concepts: non-trivial informational closure and neural coarse- graining. In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents. We next argue that through coarse-graining the human neural system can achieve non-trivial informational closure at a specific coarse-grained level. We then propose that the state of the informational closure correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory. We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness. Finally, we provide predictions and testable approaches for this theory.

		% TODO: is figure needed?
		\idea{Do I need a figure?, Something like this one?}
		\begin{figure}[H]
			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
			\cite{pennartz2017consciousness}
			\caption{xxxx}
	   	\end{figure}
